\section{Methodology}\label{sec:methodology}

The sample dataset was built by making a search at Xinhua's English
language website at \url{http://www.xinhuanet.com/english/} for the
string ``Duterte'' and downloading all the news articles returned by the
result pages. This search string forms the basis of the whole dataset.
The latest news article is on November 11, 2016.

Articles that had the word ``Duterte'' but did not specifically refer to
Rodrigo Duterte were removed from the analysis dataset. Articles that
were included in the results but did not mention Duterte on the first
page are also pruned. There are also ``news summaries'' present in the
download, summarizing the week's world news in a single article. Those
items were also pruned. Despite the removal of these articles, I have
not removed them from the download for completeness.

To make this possible, a routine was performed to automate the
download of news articles returned by the search operation. A small
script (see appendix \ref{adx:python-script}) was written to automate
the cleanup and extraction of the news article full text. Part of the
data extracted includes filename, date of publication, title, and
body text.

In analyzing the data, a simple thematic analysis was performed. News
articles were read individually and then tagged according to a general
theme such as but not limited to ``foreign relations'' for articles that
involve two or more countries and their diplomatic relations, ``war on
drugs'' for articles that refer to the Duterte Administration's
flagship policy on eliminating illegal drugs in the country, and
``national issues'' for articles that talk about domestic controversies
and problems.

As a secondary analysis, text mining was done through the free version
of RapidMiner 7.3, generating bigrams and trigrams\footnote{Sets of
words in twos or threes}, and individual word counts. These statistics
may give us an idea what topics were talked about, and what words were
frequently used during these two news periods. However, these
statistics are not indicative of any sentiment or value judgement from
any party involved.

All assets used in data gathering, results, and a description of the
working environment are available in a GitHub repository at
\href{https://github.com/tsdmgz/xinhua-duterte-coverage}{github.com/tsdmgz/xinhua-duterte-coverage}.

\section{Limitations}\label{sec:limits}

For manageability, I have limited the data to the following events: the
Hague Ruling on the South China Sea dispute, and President Duterte's
first state visit to China. Specifically, these dates are July 5, 2016
until July 19, 2016 for the Hague Ruling, and October 11, 2016 until
October 28, 2016, inclusive.

These were chosen because these two events carry significant weight in
China-Philippines bilateral relations. However, the articles present in
the dataset is not comprehensive as the articles on these dates are
those which has referred to President Duterte at least once.

% vim: tw=72 smartindent breakindent syntax=tex
